\chapter{geometry}

\codeWithDescription{Point 2D}{geometry/Point.h}
[Description: Class to handle points in the plane. T can be e.g. double or long long. (Avoid int.)]

\codeWithDescription{Line Intersection}{geometry/lineIntersection.h}%
[If a unique intersection point of the lines going through s1,e1 and s2,e2 exists \{1, point\} is returned. 
If no intersection point exists \{0, (0,0)\} is returned and if infinitely many exists \{-1, (0,0)\} is returned. 
The wrong position will be returned if P is Point<ll> and the intersection point does not have integer coordinates. 
Products of three coordinates are used in intermediate steps so watch out for overflow if using int or ll.]%
[graphics/geometry/lineIntersection]
[
    auto res = lineInter(s1,e1,s2,e2);
 	if (res.first == 1)
		cout << "intersection point at " << res.second << endl;
]

\codeWithDescription{Segment Distance}{geometry/SegmentDistance.h}
[Returns the shortest distance between point p and the line segment from point s to e.]
[graphics/geometry/SegmentDistance]
[
    Point<double> a, b(2,2), p(1,1);
 	bool onSegment = segDist(a,b,p) < 1e-10;
]

\codeWithDescription{Segment Intersection}{geometry/SegmentIntersection.h}
[
If a unique intersection point between the line segments going from s1 to e1 and from s2 to e2 exists then it is returned.
If no intersection point exists an empty vector is returned.
If infinitely many exist a vector with 2 elements is returned, containing the endpoints of the common line segment.
The wrong position will be returned if P is Point<ll> and the intersection point does not have integer coordinates.
Products of three coordinates are used in intermediate steps so watch out for overflow if using int or long long.
]
[graphics/geometry/SegmentIntersection]
[vector<P> inter = segInter(s1,e1,s2,e2);
 if (sz(inter)==1)
   cout << "segments intersect at " << inter[0] << endl;
]

\codeWithDescription{Side Of}{geometry/sideOf.h}
[
 Returns where $p$ is as seen from $s$ towards $e$. 1/0/-1 $\Leftrightarrow$ left/on line/right.
 If the optional argument $eps$ is given 0 is returned if $p$ is within distance $eps$ from the line.
 P is supposed to be Point<T> where T is e.g. double or long long.
 It uses products in intermediate steps so watch out for overflow if using int or long long.
]
[]
[bool left = sideOf(p1,p2,q)==1;]

\codeWithDescription{On Segment}{geometry/OnSegment.h}
[Returns true iff p lies on the line segment from s to e.]
[]
[\texttt{(segDist(s,e,p)<=epsilon)} instead when using Point<double>.]

\codeWithDescription{Linear Transformation}{geometry/linearTransformation.h}
[Apply the linear transformation (translation, rotation and scaling) which takes line p0-p1 to line q0-q1 to point r.]
[graphics/geometry/linearTransformation]

\codeWithDescription{Angle class}{geometry/Angle.h}
[A class for ordering angles (as represented by int points and  a number of rotations around the origin). 
Useful for rotational sweeping. Sometimes also represents points or vectors.]%
[]
[vector<Angle> v = {w[0], w[0].t360() ...}; // sorted
  int j = 0; rep(i,0,n) { while (v[j] < v[i].t180()) ++j; }
  // sweeps j such that (j-i) represents the number of positively oriented triangles with vertices at 0 and i
]

\codeWithDesciption{Circle Intersection}{geometry/CircleIntersection.h}
[Computes the pair of points at which two circles intersect. Returns false in case of no intersection.]

\codeWithDescription{Circle Tangents}{geometry/CircleTangents.h}
[Finds the external tangents of two circles, or internal if r2 is negated.
 Can return 0, 1, or 2 tangents -- 0 if one circle contains the other (or overlaps it, in the internal case, or if the circles are the same);
 1 if the circles are tangent to each other (in which case .first = .second and the tangent line is perpendicular to the line between the centers).
 .first and .second give the tangency points at circle 1 and 2 respectively.
 To find the tangents of a circle with a point set r2 to 0. O(n)
 ]

 \codeWithDescription{Minimum Enclosing Circle}{geometry/MinimumEnclosingCircle.h}
 [Computes the minimum circle that encloses a set of points. O(n)]

 \codeWithDescription{Inside Polygon}{geometry/InsidePolygon.h}
 [
 Returns true if p lies within the polygon. If strict is true, it returns false for 
 points on the boundary. The algorithm uses products in intermediate steps so watch out for overflow. O(n)
 ]
 []
 [vector<P> v = {P{4,4}, P{1,2}, P{2,1}};
 bool in = inPolygon(v, P{3, 3}, false);
 ]

\codeWithDescription{Polygon Area}{geometry/PolygonArea.h}
[Returns twice the signed area of a polygon. Clockwise enumeration gives negative area. 
Watch out for overflow if using int as T!]

\codeWithDescription{Polygon Center}{geometry/PolygonCenter.h}
[Returns the center of mass for a polygon. Time: O(n)]

\codeWithDescription{Convex Hull}{geometry/ConvexHull.h}
[Returns a vector of the points of the convex hull in counter-clockwise order.
Points on the edge of the hull between two other points are not considered part of the hull. O(nlogn)
]%
% [graphics/geometry/ConvexHull]
% []

\codeWithDescription{Hull Diameter}{geometry/HullDiameter.h}
[Returns the two points with max distance on a convex hull (ccw, no duplicate/collinear points). O(n)]

\codeWithDescription{Point Inside Hull}{geometry/PointInsideHull.h}
[
 Determine whether a point t lies inside a convex hull (CCW
 order, with no collinear points). Returns true if point lies within
 the hull. If strict is true, points on the boundary aren't included. O(logN)
]

\codeWithDescription{Line Hull Intersection}{geometry/LineHullIntersection.h}
[Line-convex polygon intersection. The polygon must be ccw and have no collinear points.
 lineHull(line, poly) returns a pair describing the intersection of a line with the polygon:
  \begin{itemize*}
    \item $(-1, -1)$ if no collision,
    \item $(i, -1)$ if touching the corner $i$,
    \item $(i, i)$ if along side $(i, i+1)$,
    \item $(i, j)$ if crossing sides $(i, i+1)$ and $(j, j+1)$.
  \end{itemize*}
  In the last case, if a corner $i$ is crossed, this is treated as happening on side $(i, i+1)$.
  The points are returned in the same order as the line hits the polygon.
 \texttt{extrVertex} returns the point of a hull with the max projection onto a line. O(logN)]

\codeWithDescription{Closest Pair}{geometry/ClosestPair.h}
[Finds the closest pair of points. O(nlogn)]

\codeWithDescription{Polyhedron Volume}{geometry/PolyhedronVolume.h}
[Magic formula for the volume of a polyhedron. Faces should point outwards.]

\codeWithDescription{Point 3D}{geometry/Point3D.h}
[lass to handle points in 3D space.	T can be e.g. double or long long.]

\codeWithDescription{3D Convex Hull}{geometry/3dHull.h}
[Computes all faces of the 3-dimension hull of a point set. *No four points must be coplanar*, or else random results will be returned. All faces will point outwards. Time: O(n^2)]

\codeWithDescription{Spherical Distance}{geometry/sphericalDistance.h}
[Returns the shortest distance on the sphere with radius radius between the points
 with azimuthal angles (longitude) f1 ($\phi_1$) and f2 ($\phi_2$) from x axis and zenith angles
 (latitude) t1 ($\theta_1$) and t2 ($\theta_2$) from z axis (0 = north pole). All angles measured
 in radians. The algorithm starts by converting the spherical coordinates to cartesian coordinates
 so if that is what you have you can use only the two last rows. dx*radius is then the difference
 between the two points in the x direction and d*radius is the total distance between the points.]