\chapter{Graph}

\code{Dijkstra}{graph/dijkstra.cpp}

\codeWithDescription{Bellmanford}{graph/bellmanford.cpp}
[Calculates shortest paths from $s$ in a graph that might have negative edge weights. Unreachable nodes get \texttt{dist = inf}; nodes reachable through negative-weight cycles get \texttt{dist = -inf}. Assumes $V^2 \max |w| < \infty$ to prevent overflow. \\
\textbf{Time:} {$O(VE)$}]

% \codeWithDescription{Biconnected Component}{graph/biconnectedcomp.cpp}
% [Finds biconnected components, bridges, and articulation points in a simple undirected graph. \\
% \textbf{Usage:} Build adj list via \texttt{ed[u].push\_back(\{v, edge\_id\})}. Call \texttt{bicomps(n, f)} where \texttt{f(comp)} is called for each component (vector of edge IDs). After call, \texttt{bridges} contains bridge edges and \texttt{isArt[i]} is 1 for articulation points. \\
% \textbf{Time:} {$O(V + E)$}]

% Added clean new bcc template
\codeWithDescription{BCC, Bridge, AP}{graph/bcc.cpp}
[Finds biconnected components, bridges, and articulation points in a simple undirected graph. \\
\textbf{Usage:} Build graph using \texttt{g[u].push\_back(\{v, edge\_id\})} and call \texttt{get\_bcc(n)}.
The vector \texttt{bccs} stores each biconnected component as a list of edge IDs.
\texttt{bridges} stores all bridge edge IDs, and \texttt{is\_art[u]} is true if node $u$ is an articulation point.
Graph must be \textbf{cleared} between test cases. \\
\textbf{Time:} {$O(V + E)$}]

\code{LCA}{graph/lca.cpp}

% \code{SCC}{graph/scc.cpp}

% Nahdi's scc
\codeWithDescription{SCC}{graph/scc_nahdi.cpp}
[Finds strongly connected components in a directed graph. 
If vertices $u, v$ belong to the same component, 
we can reach $u$ from $v$ and vice versa.]
[]
[scc(graph, (vi& v) { ... }) visits all components
 in reverse topological order. comp[i] holds the component
 index of a node (a component only has edges to components with
 lower index). ncomps will contain the number of components. O(E+V)]

\code{HLD}{graph/hld.cpp}
% \code{Heavy Light Decomposition}{graph/hld_nahdi.cpp}

\code{Centroid Decomposition}{graph/cd.cpp}