\chapter{String}

\code{Trie}{string/trie.cpp}

\code{Bit Trie}{string/bit_trie.cpp}

\code{Z Algorithm}{string/zalgo.cpp}

\codeWithDescription{KMP}{string/KMP.h}
[pi[x] computes the length of the longest prefix of s that ends at x, other than s[0...x] itself (abacaba -> 0010123).
 Can be used to find all occurrences of a string. Time: O(n)]

\codeWithDescription{Suffix Array}{string/SuffixArray.h}
[Builds suffix array for a string. \texttt{sa[i]} is the starting index of the suffix which
 is $i$'th in the sorted suffix array. The returned vector is of size $n+1$, and \texttt{sa[0] = n}.
 The \texttt{lcp} array contains longest common prefixes for neighbouring strings in the suffix array:
 \texttt{lcp[i] = lcp(sa[i], sa[i-1])}, \texttt{lcp[0] = 0}. The input string must not contain any nul chars.
 Time: O(nlogn)
 ]

\codeWithDescription{Manacher}{string/Manacher.h}
[
    For each position in a string, computes p[0][i] = half length of longest even 
    palindrome around pos i, p[1][i] = longest odd (half rounded down). Time: O(N)
]

\codeWithDescription{Aho Corasick}{string/AhoCorasick.h}
[
    Aho-Corasick automaton, used for multiple pattern matching. Initialize with 
    AhoCorasick ac(patterns); the automaton start node will be at index 0. find(word) returns 
    for each position the index of the longest word that ends there, or -1 if none. findAll($-$, word) 
    finds all words (up to $N \sqrt N$ many if no duplicate patterns) that start at each position 
    (shortest first). Duplicate patterns are allowed; empty patterns are not. To find the longest 
    words that start at each position, reverse all input. For large alphabets, split each symbol into 
    chunks, with sentinel bits for symbol boundaries. Time: construction takes $O(26N)$, 
    where $N =$ sum of length of patterns. find(x) is $O(N)$, where N = length of x. findAll is $O(NM)$
]

\code{Hashing}{string/hashing.h}